---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/rtide.svg?branch=master)](https://travis-ci.org/poissonconsulting/rtide)
[![AppVeyor Build status](https://ci.appveyor.com/api/projects/status/598p54bq0m5qv0j1/branch/master?svg=true)](https://ci.appveyor.com/project/joethorley/rtide/branch/master)
[![codecov](https://codecov.io/gh/poissonconsulting/rtide/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/rtide)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rtide)](https://cran.r-project.org/package=rtide)
[![CRAN Downloads](http://cranlogs.r-pkg.org/badges/grand-total/rtide)](https://cran.r-project.org/package=rtide)

# rtide

## Introduction

`rtide` is an R package to calculate tide heights.

The included rtide object `noaa` includes the harmonics for `r sum(!is.na(rtide::noaa$stations$Datum))` reference, and the offsets for `r sum(is.na(rtide::noaa$stations$Datum))` secondary, NOAA tide stations.

The `noaa` harmonics and offsets were scrapped from <https://tidesandcurrents.noaa.gov> on April 5, 2017.

## Utilisation

```{r, message=FALSE}
library(magrittr)
library(stringr)
library(dplyr)
```

```{r}
library(rtide)

stations <- rtide::noaa$stations
stations %<>% filter(str_detect(StationName, "Santa Barbara"))
stations

datetime <- seq_datetime(from = as.Date("2016-07-13"), minutes = 10L, tz = "PST8PDT")

data <- expand.grid(Station = stations$Station, DateTime = datetime, stringsAsFactors = FALSE) %>% as.tbl()
data

#data %<>% predict_rtide(rtide = rtide::noaa)

```

```{r, message=FALSE}
library(ggplot2)
library(scales)
```

```
ggplot(data = data, aes(x = DateTime, y = TideHeight)) + 
  geom_line() + 
  scale_x_datetime(name = "Date", 
                   labels = date_format("%d %b %Y", tz="PST8PDT")) +
  scale_y_continuous(name = "Tide Height (m)") +
  ggtitle("Monterey Harbour")
```

## Installation

To install the release version from CRAN
```
install.packages("rtide")
```

Or the development version from GitHub
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/rtide")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/rtide/issues).

[Pull requests](https://github.com/poissonconsulting/rtide/pulls) are always welcome.

## Inspiration

The code to calculate tide heights from the harmonics is inspired by XTide.

The `harmonics` object which has been deprecated for the `noaa` object was converted from harmonics-dwf-20151227-free, NOAA web site data
processed by David Flater for [XTide](http://www.flaterco.com/xtide/).
